\newglossaryentry{DSP} {name=DSP,description={Digital Signal Processing}}
\newglossaryentry{COTS} {name=COTS,description={Commercial Off The Shelf}}
\newglossaryentry{FPGA} {name=FPGA,description={Field Programmable Array}}
\newglossaryentry{ARM} {name=ARM,description={Processor architecture based on a reduced instruction set computing architecture}}
\newglossaryentry{IC} {name=IC,description={Integrated Circuit}}
\newglossaryentry{ADC} {name=ADC,description={Analog to digital converter}}
\newglossaryentry{eV} {name=eV,description={Electron volt $\unit{1}{eV}=\unit{1.602\times10^{-19}}{C}$}}
\newglossaryentry{MeV} {name=MeV,description={Mega electron volt ($10^6$)}}
\newglossaryentry{keV} {name=keV,description={Kilo electron volt ($10^3$)}}
\newglossaryentry{GeV} {name=GeV,description={Giga electron volt ($10^9$)}}
\newglossaryentry{TeV} {name=TeV,description={Tera electron volt ($10^12$)}}
\newglossaryentry{CERN} {name=CERN,description={European Organization for Nuclear Research}}
\newglossaryentry{ALICE} {name=ALICE,description={A Large Ion Collider Experiment}}
\newglossaryentry{LHC} {name=LHC,description={Large Hadron Collider}}
\newglossaryentry{ALTRO} {name=ALTRO,description={ALICE TPC Read Out}}
\newglossaryentry{MSPS} {name=MSPS,description={Mega Samples Per Second}}
\newglossaryentry{DPP} {name=DPP,description={Digital Pulse Processing}}
\newglossaryentry{LVDS} {name=LVDS,description={Low-voltage differential signaling}}
\newglossaryentry{GPIO} {name=GPIO,description={General-purpose input/output}}
\newglossaryentry{I2C} {name=I2C,description={A multi-master multi-slave, single ended serial bus}}
\newglossaryentry{PCB} {name=PCB,description={Printed Circuit Board}}
\newglossaryentry{VHDL} {name=VHDL,description={VHSIC Hardware Description Language}}
\newglossaryentry{TID} {name=TID,description={Total Ionizing Dose}}
\newglossaryentry{CMOS} {name=CMOS,description={Complementary metal–oxide–semiconductor}}
\newglossaryentry{Cf} {name=$\prescript{\bf{252}}{}{\bf{Cf}}$,description={Californium-252, A widely used radiation source that undergoes spontaneous fission}}
\newglossaryentry{Am} {name=$\prescript{\bf{241}}{}{\bf{Am}}$,description={Americium-241, Alpha radiation source commonly used for calibrating radiation sources}}
\newglossaryentry{LT} {name=LT,description={Linear Technology}}
\newglossaryentry{SPICE} {name=SPICE,description={Simulation Program with Integrated Circuit Emphasis}}
\newglossaryentry{LTspice} {name=LTspice,description={Linear Technology Simulation Program with Integrated Circuit Emphasis}}
\newglossaryentry{SINTEF} {name=SINTEF,description={An independant Norwegian reasearch organization}}
\newglossaryentry{PIN diode} {name=PIN diode,description={A diode with a wide undoped semiconductor region between the p- and n- type semiconductor}}
\newglossaryentry{FIFO} {name=FIFO,description={First In First Out}}
\newglossaryentry{MSB} {name=MSB,description={Most Significant Bit}}
\newglossaryentry{LSB} {name=LSB,description={Least Significant Bit}}
\newglossaryentry{SPI} {name=SPI,description={Serial Peripheral Interface bus, a synchrounus serial communication interface.}}
\newglossaryentry{DUT} {name=DUT,description={Device Under Test.}}
\newglossaryentry{OOP} {name=OOP,description={Object-Oriented Programming.}}
\newglossaryentry{TB} {name=TB,description={Test Bench.}}
\newglossaryentry{kBq} {name=kBq,description={Kilo Becquerel. One Becquerel is the activity of a radioactive material which undergoes one nuclear decay per second.}}
\newglossaryentry{FWHM} {name=FWHM,description={Full Width at Half Maximum. Difference between the two values of the independent variable where the dependent variable is at half of its maximum.}}
\newglossaryentry{HPS} {name=HPS,description={Hard Processor System. A processor implemented in CMOS as opposed to soft processors which are implemented in FPGA fabric.}}
\newglossaryentry{SD-card} {name=SD-card,description={Secure Digital nonvolatile solid state memory card.}}
\newglossaryentry{scp} {name=scp,description={Secure copy, a remote file copy program.}}
\newglossaryentry{NFS} {name=NFS,description={Network File System, a distributed file system protocol.}}
\newglossaryentry{MCU} {name=MCU,description={Microcontroller Unit}}
\newglossaryentry{SEL} {name=SEL,description={Single Event Latchup}}
\newglossaryentry{SEU} {name=SEU,description={Single Event Upset}}
\newglossaryentry{SEE} {name=SEE,description={Single Event Effect}}
\newglossaryentry{MBU} {name=MBU,description={Multi Bit Upset}}
\newglossaryentry{SEFI} {name=SEFI,description={Single Event Functional Interrupt}}
\newglossaryentry{EEPROM} {name=EEPROM,description={Electrically erasable programmable read-only memory}}
\newglossaryentry{PSI} {name=PSI,description={The Paul Scherrer Institute, the largest research institute for natural and engineering sciences within Switzerland}}
\newglossaryentry{KVI} {name=KVI,description={Kernfysisch Versneller Instituut, leading Dutch institute in the fields of fundamental and applied subatomic and atomic physics}}
